Empty Homes V1

### 2017-06-02 EmptyHomesV1.Rmd
Chelsea Analysis
Added some code which performs an analysis for Chelsea.

@@

@@

Newhaminfo <- read.xlsx( "NewhamExemptionsLSOA.XLSX"  , colNames = TRUE)[,1:4] %>%
  StructureData(2)

@@

@@

sum(Chelseainfo$MeanPrice*Chelseainfo$counts)/sum(Chelseainfo$counts)

prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))

@@

@@

corplotter(Chelseainfo, "MedianPrice", "WardLowUsePerc", "Median Price vs Low Use % by ward in RBKC",
           "Low Use Percentage by Ward",
           "Median Price")
SaveFig("ChelseaCor.png")

>>>>

man-whitney

@@

#savils definitions of prime also there segmentation of the market
http://pdf.euro.savills.co.uk/spotlight-on/spotlight-on-london-housing-supply.pdf

@@

Newhaminfo <- read.xlsx( "NewhamDiscountsLSOA.xlsx", colNames = TRUE)[,1:4] %>%
  StructureData(full = F)

@@

test <-  Chelseainfo %>% left_join(., AG)

@@

#T test if there is a significant difference between 
v <- Chelseainfo %>% filter(LAD11CD =="E09000020")

#low-use value chelsea
sum(v$MeanPrice*v$LowUse)
ChelMeanPrice <- (sum(v$MeanPrice*v$counts)/sum(v$counts))
ChelLowMean<- sum(v$MeanPrice*v$LowUse)/sum(v$LowUse)
ChelLowMean/ChelMeanPrice
v<- rep(v$MeanPrice, times = v$LowUse)-ChelMeanPrice

t.test(v,alternative = "greater")

prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))
Admin_ward_code
#c("Lower Mainstream", "Mid Mainstream", "Upper Mainstream", "Prime", "Super Prime"),
test <- prices %>% 
  filter( Admin_district_code =="E09000020") %>%
  mutate(class = cut(X2, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
             right = F)) %>%
  select(Admin_ward_code, class) %>%
  group_by(Admin_ward_code, class) %>% 
  summarise(Counts = n()) %>%
  group_by(Admin_ward_code) %>%
  mutate(WardPerc = Counts/sum(Counts)) %>%
  ungroup

test3 <- Chelseainfo %>% 
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first)) %>%
  select(Admin_ward_code, WardLowUse, WardHomes) %>%
  left_join(., test, "Admin_ward_code") %>%
  mutate(LowUseClass = WardLowUse*WardPerc,
         HomesClass = WardHomes*WardPerc) %>%
  group_by(class) %>%
  summarise(LowUseClass = sum(LowUseClass),
            HomesClass = sum(HomesClass)) %>%
  filter(complete.cases(.)) %>%
  mutate(PercOfLowUse = LowUseClass/sum(LowUseClass),
         PercOfHomes = HomesClass/sum(HomesClass),
         PercofClass = LowUseClass/HomesClass)

#Percentage over and under of what would be expected if buying was random
#The differences suggest that people are buying more expensive homes when there is no plan to live in them.
round(test3$LowUseClass/(sum(test3$LowUseClass)*test3$PercOfHomes),2)
```

@@

Value of low*use and total low use
```{r}

test <-  ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
  group_by(Admin_ward_code) %>%
  summarise(LAD11NM = first(LAD11NM),
            MeanPrice = first(MeanPrice),
            WardLowUse = first(WardLowUse)) %>%
  group_by(LAD11NM) %>%
  summarise(totalLow = sum(MeanPrice*WardLowUse)/1e6,
            TotalEmpt = sum(WardLowUse))

sum(test$totalLow, na.rm = T)  
sum(test$TotalEmpt, na.rm = T)  
length(unique(test$LAD11NM))

@@

corplotter(Chelseainfo, "MeanPrice", "WardLowUsePerc", "Mean Price vs Low Use % by ward in RBKC",
           "Low Use Percentage by Ward",
           "Mean Price")
SaveFig("ChelseaCor.png")

Chelseainfo %>% filter(WardLowUsePerc != max("WardLowUsePerc"),
                       MeanPrice != max(MeanPrice)) %>%
  corplotter(., "MeanPrice", "WardLowUsePerc", "Median Price vs Low Use % by ward in RBKC",
           "Low Use Percentage by Ward",
           "Median Price")
```
